An open library of human kinase domain constructs for automated bacterial expression

### 2016-02-02 manuscript/ms.tex
added a bit more text to results section

\begin{figure}[tb]
   \includegraphics[width=\columnwidth]{figures/ncandidates_byfamily.png}
  \caption{{\bf Histogram of kinases in panel by family.}
   Plot of 96 kinases expressed in the expression panel, separated out by family.
   }
  \label{fig:calliper_image}
\end{figure}

@@

A panel containing the 96 kinase domain constructs selected through our semi-automated method, was tested for expression in E. coli. 
From this initial test, 68 kinase domains expressed successfully (yield of more than 2 ng/$\mu$L ).

@@

\bf{kinase expressed} & \bf{phosphatase co-expressed} & \bf{concentration ($ng/ \mu l$)} \\

>>>>

Selecting the kinases and their constructs for this expression trial was primarily on the basis of expected success: these specific kinase constructs previously expressed and purified easily enough that a crystal structure could be solved.
While the final expression and characterization of these kinases was our ultimate goal, the patterns that popped up via the use of our semi-automated pipeline are also worth noting.
The most highly sampled family in our final panel, for example, was the CAMK family (Figure~\ref{fig:kinases_by_family}).

\begin{figure}[tb]
   \includegraphics[width=\columnwidth]{figures/ncandidates_byfamily.png}
  \caption{{\bf Distribution of kinases in final expression panel by family.}
   Histogram of the 96 kinases expressed in the expression panel, separated out by kinase family.
   }
  \label{fig:kinases_by_family}
\end{figure}

@@

A panel containing the 96 kinase domain constructs selected through our semi-automated method, was tested for expression in E. coli. 
From this initial test, 68 kinase domains expressed successfully (yield of more than 2 ng/$\mu$L ) (Table~\ref{expression_table}).
While the initial panel of 96 kinases was well-distributed across kinase families, the final most highly expressing (yield of more than 100 ng/$\mu$L ) were not as evenly distributed (Figure~\ref{fig:kinome_expression_tree}). 
The 17 most highly expressing kinases all were quite pure with some TEV contaminants still present in Calliper gel images after elution with Imidazole (Figure~\ref{fig:calliper_image}).

@@

\bf{kinase expressed} & \bf{phosphatase co-expressed} & \bf{concentration (ng/$\mu$l)} \\
